Categorical Predictor Embeddings in Actuarial Modeling

### 2020-11-17 manuscript/manuscript.Rmd
Added NN section

---
title: Categorical Predictor Embeddings in Actuarial Modeling
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevin@kasa.ai
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants
    email: ronaldrichman@gmail.com
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
output: rticles::arxiv_article
---

@@

The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modelling concepts. In Section \ref{modelling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model. Section \ref{tl} considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data. Extensions to the modelling approach are considered in Section \ref{extend} and we focus on attention based models in Section \ref{attention}. The interpretability of embedding layers is addressed in Section \ref{interpretation}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper and considers avenues for future research.

@@

We will use mainly use GLMs and neural networks to approximate the function $f(.)$.

@@

A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels. Let the set of labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ is the cardinality or number of levels, in $\mathcal{P}^j$. One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise. An example of one-hot encoding is shown in Table \ref{tab:onehot}.

@@

# nfip = cellar_pull("nfip_claims", vintage = NULL)
# 
# states = nfip %>% select(state) %>% unique()
# 
# states %>% fwrite("manuscript/states.csv")

states= fread("../manuscript/states.csv")

@@

dummies <- rec %>% step_dummy(state)
dummies <- prep(dummies, training = sample_dat)

@@

cbind(sample_dat, dummy_data) %>% knitr::kable(label = "tab:onehot", caption = "Example one-hot encoding of the state variable")
```

One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables.

The approach that we focus on in this study is to use embeddings, which map each level of the categorical data to a low dimensional vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling problem. Formally, an embedding is

@@

where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is an function that maps from the particular element of the labels $p$ to the embedding space. This function is left implicit, meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to specify exactly how the embeddings can be derived from the input data.

## Predictive Modeling with GLM and a Minimalist Neural Network

@@

\begin{equation}
x \mapsto \log(1 + e^x).
\end{equation}

@@

# Attention based modelling {#attention}

>>>>

---
title: Categorical Predictor Embeddings in Actuarial Modeling
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevin@kasa.ai
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants
    email: ronaldrichman@gmail.com
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
output: rticles::arxiv_article 
extra_dependencies: ["amsmath"]

---

@@

The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modelling concepts, including embeddings and attention. In Section \ref{modelling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model. Section \ref{tl} considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data. Extensions to the modelling approach are considered in Section \ref{extend} and we focus on attention based models in Section \ref{attention}. The interpretability of embedding layers is addressed in Section \ref{interpretation}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper and considers avenues for future research.

@@

In this study, will use mainly use GLMs and neural networks to approximate the function $f(.)$.

@@

A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels. Let the set of labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ is the cardinality or number of levels, in $\mathcal{P}^j$. One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise. An example of one-hot encoding is shown in Table \ref{onehot}.

@@

states= fread("../manuscript/states.csv")
set.seed(42)
sample_dat = sample_n(states,5) %>% arrange(state)

dummies <- rec %>% step_dummy(state, one_hot =T)
dummies <- prep(dummies, training = sample_dat)

cbind(sample_dat, dummy_data) %>% knitr::kable(label = "onehot", caption = "Example one-hot encoding of the state variable")
```

One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables. An example of dummy encoding is shown in Table \ref{dummy}.

```{r, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}

states= fread("../manuscript/states.csv")
set.seed(42)

@@

dummies <- rec %>% step_dummy(state, one_hot =F)
dummies <- prep(dummies, training = sample_dat)

@@

cbind(sample_dat, dummy_data) %>% knitr::kable(label = "dummy", caption = "Example dummy encoding of the state variable")

```

After encoding the categorical data in this manner, most regression models such as GLMs will then fit coefficients for each level of the category in the table (if a tree based model is used, such as decision tree, then splits in the tree may occur depending on the presence, or not, of the categorical variable for the data). If one-hot encoding has been used, $n_\mathcal{P}^j$ coefficients will be fit, compared to $n_\mathcal{P}^j - 1$ coefficients in the case of dummy coding.

These coefficients represent the effect that each level of the categorical variable will have on the outcome. In the case that there are no other variables available in the dataset, then the coefficients will reflect the average value of the outcomes for that level of the categorical variable. For example, suppose that the categorical variable is a policyholder identifier, and the outcomes are the value of claims in different years, then the coefficients will reflect the average annual claims for each policyholder based on the experience. In other words, both of these encoding schemes give full credibility to the data available for each category, thus, even if a relatively small amount of data is available for a specific policyholder, the coefficient that is calibrated will only reflect that data. On the other hand, a foundational technique within actuarial work is the application of credibility methods, which are used for experience rating and other applications. These techniques provide an estimate that reflects not only the experience of the individual policyholder but also that of the collective, based on an estimate of how credible the data for each individual is. While we have described the application of credibility in a simple univariate context, it is also possible to apply credibility considerations within GLMs. using models known as Generalized Linear Mixed Models or GLMMs, and we refer to [@Klinker2010] for more details.

Having described traditional approaches for modeling categorical data, we now turn to neural networks, and discuss embedding layers for categorical data modeling, which we define in more detail in the section on neural networks.

## Neural Networks

Neural networks are flexible machine learning models that have recently been applied to a number of problems with Property and Casualty (P&C) insurance. Here, we provide a brief overview of these models, and refer the reader to [@Richman2018] for a more detailed overview. Neural networks are characterized by multiple layers of non-linear regression functions that are used to learn a new representation of the data input to the network that is then used to make predictions. Here we focus on the most common type of neural networks, which are fully connected networks (FCNs), which provide as the output of each set of non-linear functions to the subsequent layer of functions. Formally, a $K$-layer neural network is:

\begin{equation} 
\label{NN}
\begin{split}
z^1 &= \sigma(a_1.X+ b_1) \\
z^2 &= \sigma(a_2.z^1+ b_2) \\
\vdots \\
z^K &= \sigma(a_{K}.z^{K-1}+ b_{K}) \\
\hat{y} &= \sigma(a_{K+1}.z^{K}+ b_{K+1}),
\end{split}
\end{equation}

where the regression parameters (weights) for each layer $$k \in [1;K]$$ are represented by the matrices $a_k$ and the intercept terms are represented by $b_k$. Whereas the calculation inside each of the layers is nothing more than linear regression, $\sigma$ represents the non-linear part of each layer. Choices for $\sigma$ are often the tanh function or the rectified linear unit (ReLu) $max(0,x)$. The parameters of the network are estimated ('trained') as follows. First a loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ and the predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$). Then, the parameters of the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).Finally, training is stopped once the predictive performance of the network on unseen data is suitably good.

If $K$ is set equal to $1$, then Equation \ref{NN} reduced to nothing more than a GLM. A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network. The matrix $X$ of data input to the network can be composed of both continuous variables as well as categorical variables, which can be pre-processed using one-hot or dummy encoding. As mentioned above, a different option is to use encodings, which we discuss in more detail next.

### Embeddings
Common issues with the traditional encoding schemes for categorical data occur when the number of levels for each variable is very large. Often, in these cases, models do not converge quickly, and the very large matrices that result from applying these schemes often cause computational difficulties. Besides for these practical issues, a deeper issue is that one-hot or dummy encoded data assumes that each category is entirely independent of the rest of the categories, in other words, there are no similarities between categories that could enable more robust estimation of models. In technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each other. (These arguments appear in a similar form in [@Guo2016].) Solutions to these problems are provided by embedding layers.

An embedding layer is a neural network component which maps each level of the categorical data to a low dimensional vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling problem. Formally, an embedding is

@@

where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is an function that maps from the particular element of the labels $p$ to the embedding space. Equation \ref{eq:embedding} states that an embedding maps a level of a categrical variable to a numerical vector. This function is left implicit, meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to specify exactly how the embeddings can be derived from the input data. In Table \ref{embed} we show an example of two dimensional embeddings for the state variables, where these have been generated randomly.

```{r, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
states= fread("../manuscript/states.csv")
set.seed(42)

data.frame(sample_dat, dimension1 = rnorm(5),dimension2 = rnorm(5)) %>% knitr::kable(label = "", caption = "Example (random) embeddings of the state variable")

```

When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be calibrated during the same fitting process that calibrates the parameters of the neural network.

### Attention {#attention}

# Predictive Modeling with GLM and a Minimalist Neural Network

@@

\\begin{equation} x \\mapsto \\log(1 + e\^x). \\end{equation}

@@

# Attention based modelling

### 2020-11-17 manuscript/manuscript.tex
Added NN section

We will use mainly use GLMs and neural networks to approximate the
function \(f(.)\).

@@

A categorical variable \(X_j, j \in J_{cat}\) takes as its value only
one of a finite number of labels. Let the set of labels be
\(\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}\),
where \(n_\mathcal{P}^j = |\mathcal{P}^j|\) is the cardinality or number
of levels, in \(\mathcal{P}^j\). One-hot encoding maps each value
\(x_{i,j}\) of \(X_j\) to \(n_\mathcal{P}^j\) indicator variables, which
take a value of \(1\) if the label of \(x_{i,j}\) corresponds to the
level of the indicator variable, and \(0\) otherwise. An example of
one-hot encoding is shown in Table \ref{tab:onehot}.

\begin{longtable}[]{@{}lrrrr@{}}
\caption{Example one-hot encoding of the state variable}\tabularnewline
\toprule
state & state\_KS & state\_OK & state\_UT & state\_WA\tabularnewline
\midrule
\endfirsthead
\toprule
state & state\_KS & state\_OK & state\_UT & state\_WA\tabularnewline
\midrule
\endhead
CO & 0 & 0 & 0 & 0\tabularnewline
KS & 1 & 0 & 0 & 0\tabularnewline
OK & 0 & 1 & 0 & 0\tabularnewline
UT & 0 & 0 & 1 & 0\tabularnewline
WA & 0 & 0 & 0 & 1\tabularnewline
\bottomrule
\end{longtable}

One-hot encoding is often used in the machine learning community while
the statistical community often favors dummy coding, which, instead of
assigning \(n_p^j\) indicator variables, assigns one of the levels of
the categories as a baseline, and maps all of the other \(n_p^j -1\)
variables to indicator variables.

The approach that we focus on in this study is to use embeddings, which
map each level of the categorical data to a low dimensional vector of
parameters that is learned together with the rest of the GLM or neural
network that is used for the modeling problem. Formally, an embedding is

@@

where \(q_\mathcal{P^j}\) is the dimension of the embedding for the
\(j\)th categorical variable and \(z_\mathcal{P^j}(.)\) is an function
that maps from the particular element of the labels \(p\) to the
embedding space. This function is left implicit, meaning to say, we
allow the embeddings to be derived during the process of fitting the
model and do not attempt to specify exactly how the embeddings can be
derived from the input data.

\hypertarget{glms-and-neural-networks}{%
\subsection{GLMs and Neural Networks}\label{glms-and-neural-networks}}

\hypertarget{modelling}{%
\section{A Minimalist Neural Network}\label{modelling}}

@@

asdf

\hypertarget{neural-net}{%
\subsection{Neural net}\label{neural-net}}

asdf

@@

\hypertarget{attention}{%
\section{Attention based modelling}\label{attention}}

>>>>

In this study, will use mainly use GLMs and neural networks to
approximate the function \(f(.)\).

@@

A categorical variable \(X_j, j \in J_{cat}\) takes as its value only
one of a finite number of labels. Let the set of labels be
\(\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}\),
where \(n_\mathcal{P}^j = |\mathcal{P}^j|\) is the cardinality or number
of levels, in \(\mathcal{P}^j\). One-hot encoding maps each value
\(x_{i,j}\) of \(X_j\) to \(n_\mathcal{P}^j\) indicator variables, which
take a value of \(1\) if the label of \(x_{i,j}\) corresponds to the
level of the indicator variable, and \(0\) otherwise. An example of
one-hot encoding is shown in Table \ref{onehot}.

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{Example one-hot encoding of the state variable}\tabularnewline
\toprule
state & state\_CA & state\_MD & state\_ND & state\_UT &
state\_WA\tabularnewline
\midrule
\endfirsthead
\toprule
state & state\_CA & state\_MD & state\_ND & state\_UT &
state\_WA\tabularnewline
\midrule
\endhead
CA & 1 & 0 & 0 & 0 & 0\tabularnewline
MD & 0 & 1 & 0 & 0 & 0\tabularnewline
ND & 0 & 0 & 1 & 0 & 0\tabularnewline
UT & 0 & 0 & 0 & 1 & 0\tabularnewline
WA & 0 & 0 & 0 & 0 & 1\tabularnewline
\bottomrule
\end{longtable}

One-hot encoding is often used in the machine learning community while
the statistical community often favors dummy coding, which, instead of
assigning \(n_p^j\) indicator variables, assigns one of the levels of
the categories as a baseline, and maps all of the other \(n_p^j -1\)
variables to indicator variables. An example of dummy encoding is shown
in Table \ref{dummy}.

\begin{longtable}[]{@{}lrrrr@{}}
\caption{Example dummy encoding of the state variable}\tabularnewline
\toprule
state & state\_MD & state\_ND & state\_UT & state\_WA\tabularnewline
\midrule
\endfirsthead
\toprule
state & state\_MD & state\_ND & state\_UT & state\_WA\tabularnewline
\midrule
\endhead
CA & 0 & 0 & 0 & 0\tabularnewline
MD & 1 & 0 & 0 & 0\tabularnewline
ND & 0 & 1 & 0 & 0\tabularnewline
UT & 0 & 0 & 1 & 0\tabularnewline
WA & 0 & 0 & 0 & 1\tabularnewline
\bottomrule
\end{longtable}

After encoding the categorical data in this manner, most regression
models such as GLMs will then fit coefficients for each level of the
category in the table (if a tree based model is used, such as decision
tree, then splits in the tree may occur depending on the presence, or
not, of the categorical variable for the data). If one-hot encoding has
been used, \(n_\mathcal{P}^j\) coefficients will be fit, compared to
\(n_\mathcal{P}^j - 1\) coefficients in the case of dummy coding.

These coefficients represent the effect that each level of the
categorical variable will have on the outcome. In the case that there
are no other variables available in the dataset, then the coefficients
will reflect the average value of the outcomes for that level of the
categorical variable. For example, suppose that the categorical variable
is a policyholder identifier, and the outcomes are the value of claims
in different years, then the coefficients will reflect the average
annual claims for each policyholder based on the experience. In other
words, both of these encoding schemes give full credibility to the data
available for each category, thus, even if a relatively small amount of
data is available for a specific policyholder, the coefficient that is
calibrated will only reflect that data. On the other hand, a
foundational technique within actuarial work is the application of
credibility methods, which are used for experience rating and other
applications. These techniques provide an estimate that reflects not
only the experience of the individual policyholder but also that of the
collective, based on an estimate of how credible the data for each
individual is. While we have described the application of credibility in
a simple univariate context, it is also possible to apply credibility
considerations within GLMs. using models known as Generalized Linear
Mixed Models or GLMMs, and we refer to (Klinker 2010) for more details.

Having described traditional approaches for modeling categorical data,
we now turn to neural networks, and discuss embedding layers for
categorical data modeling, which we define in more detail in the section
on neural networks.

\hypertarget{neural-networks}{%
\subsection{Neural Networks}\label{neural-networks}}

Neural networks are flexible machine learning models that have recently
been applied to a number of problems with Property and Casualty (P\&C)
insurance. Here, we provide a brief overview of these models, and refer
the reader to (Richman 2018) for a more detailed overview. Neural
networks are characterized by multiple layers of non-linear regression
functions that are used to learn a new representation of the data input
to the network that is then used to make predictions. Here we focus on
the most common type of neural networks, which are fully connected
networks (FCNs), which provide as the output of each set of non-linear
functions to the subsequent layer of functions. Formally, a \(K\)-layer
neural network is:

\begin{equation} 
\label{NN}
\begin{split}
z^1 &= \sigma(a_1.X+ b_1) \\
z^2 &= \sigma(a_2.z^1+ b_2) \\
\vdots \\
z^K &= \sigma(a_{K}.z^{K-1}+ b_{K}) \\
\hat{y} &= \sigma(a_{K+1}.z^{K}+ b_{K+1}),
\end{split}
\end{equation}

where the regression parameters (weights) for each layer \[k \in [1;K]\]
are represented by the matrices \(a_k\) and the intercept terms are
represented by \(b_k\). Whereas the calculation inside each of the
layers is nothing more than linear regression, \(\sigma\) represents the
non-linear part of each layer. Choices for \(\sigma\) are often the tanh
function or the rectified linear unit (ReLu) \(max(0,x)\). The
parameters of the network are estimated (`trained') as follows. First a
loss function \(L(.,.)\) is specified for the network that measures the
difference between the observed data \(y\) and the predictions of the
network \(\hat{y}\), for example, the Mean Squared Error
(\((y - \hat{y})^2\)). Then, the parameters of the network are changed
such that the loss decreases (formally, this is done using the technique
of backpropagation).Finally, training is stopped once the predictive
performance of the network on unseen data is suitably good.

If \(K\) is set equal to \(1\), then Equation \ref{NN} reduced to
nothing more than a GLM. A neural network with \(K=2\) is called a
shallow neural network and for \(K \geq 2\), the network is called a
deep neural network. The matrix \(X\) of data input to the network can
be composed of both continuous variables as well as categorical
variables, which can be pre-processed using one-hot or dummy encoding.
As mentioned above, a different option is to use encodings, which we
discuss in more detail next.

\hypertarget{embeddings}{%
\subsubsection{Embeddings}\label{embeddings}}

Common issues with the traditional encoding schemes for categorical data
occur when the number of levels for each variable is very large. Often,
in these cases, models do not converge quickly, and the very large
matrices that result from applying these schemes often cause
computational difficulties. Besides for these practical issues, a deeper
issue is that one-hot or dummy encoded data assumes that each category
is entirely independent of the rest of the categories, in other words,
there are no similarities between categories that could enable more
robust estimation of models. In technical terms, this is because the
columns of the matrices created by one-hot encoding are all orthogonal
to each other. (These arguments appear in a similar form in (Guo and
Berkhahn 2016).) Solutions to these problems are provided by embedding
layers.

An embedding layer is a neural network component which maps each level
of the categorical data to a low dimensional vector of parameters that
is learned together with the rest of the GLM or neural network that is
used for the modeling problem. Formally, an embedding is

@@

where \(q_\mathcal{P^j}\) is the dimension of the embedding for the
\(j\)th categorical variable and \(z_\mathcal{P^j}(.)\) is an function
that maps from the particular element of the labels \(p\) to the
embedding space. Equation \ref{eq:embedding} states that an embedding
maps a level of a categrical variable to a numerical vector. This
function is left implicit, meaning to say, we allow the embeddings to be
derived during the process of fitting the model and do not attempt to
specify exactly how the embeddings can be derived from the input data.
In Table \ref{embed} we show an example of two dimensional embeddings
for the state variables, where these have been generated randomly.

\begin{longtable}[]{@{}lrr@{}}
\caption{Example (random) embeddings of the state
variable}\tabularnewline
\toprule
state & dimension1 & dimension2\tabularnewline
\midrule
\endfirsthead
\toprule
state & dimension1 & dimension2\tabularnewline
\midrule
\endhead
CO & 1.5115220 & 2.2866454\tabularnewline
DC & -0.0946590 & -1.3888607\tabularnewline
ME & 2.0184237 & -0.2787888\tabularnewline
PA & -0.0627141 & -0.1333213\tabularnewline
UT & 1.3048697 & 0.6359504\tabularnewline
\bottomrule
\end{longtable}

When applying embeddings in a data modeling context using neural
networks, the values of the embeddings will be calibrated during the
same fitting process that calibrates the parameters of the neural
network.

\hypertarget{attention}{%
\subsubsection{Attention}\label{attention}}

\hypertarget{predictive-modeling-with-glm-and-a-minimalist-neural-network}{%
\section{Predictive Modeling with GLM and a Minimalist Neural
Network}\label{predictive-modeling-with-glm-and-a-minimalist-neural-network}}

@@

We fit a GLM with the following specifications:

\begin{itemize}
\item
  Target variable: Amount paid on building claim
\item
  Predictors: \emph{Log} of \textbf{building insurance coverage},
  \textbf{basement enclosure type}, \textbf{number of floors in the
  insured building}, \emph{prefix} of \textbf{flood zone}, and
  \textbf{\emph{primary residence}}.
\item
  Link function: log
\item
  Distribution: gamma
\end{itemize}

We take the log of the continuous predictor \textbf{building insurance
coverage} following (cite cas glm monograph), which allows the scale of
the predictor to match that of the target variable. Because the
\textbf{flood zone} variable in the original data contains 60 levels, we
take the prefix of the zone code, which corresponds to the level of risk
as determined by FEMA (source?). For example, \emph{A01}, \emph{A02},
and so on are recoded as simply \emph{A}.

A log link together with the gamma distribution is a standard choice for
severity modeling, which provides a multiplicative structure where the
response is positive.

\hypertarget{a-simple-neural-network}{%
\subsection{A Simple Neural Network}\label{a-simple-neural-network}}

(Note: this section is WIP doesn't match up w/ code, which is also WIP)
For the neural net, we utilize the same responsible variable, amount
paid on building claim. We normalize the numeric variable
\textbf{\emph{building insurance coverage}}, one-hot encode the
\textbf{primary residence} variable, and apply embedding layers of
dimension one to the rest of the categorical variables. We then connect
the embeddings and the normalized variable to a single output unit with
softplus activation, where the softplus function is defined to be

\textbackslash begin\{equation\} x \textbackslash mapsto
\textbackslash log(1 + e\^{}x). \textbackslash end\{equation\}

Figure (todo: add figure) exhibits the architecture of our simple neural
network.

@@

\hypertarget{attention-based-modelling}{%
\section{Attention based modelling}\label{attention-based-modelling}}
